---
title: "Manuscript Analyses"
author: "Yoona Kang"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

# load packages
```{r}
library("lme4")
library("lmerTest")
library("ggplot2")
library("Rcpp")
library("lm.beta")
library("psych")
library('knitr')
library('tidyverse')
library(interactions)
library(dplyr)
library(tidyr)
library(corrplot)
```

# load data
```{r}
df <- read.csv('covid19_study1_clean_wide.csv', stringsAsFactors = FALSE)
```

# clean data
```{r}
#calculate purpose average scores

df$purpose_2r <- ifelse(df$purpose_2 == 6,1,
                           ifelse(df$purpose_2 == 5,2,
                                  ifelse(df$purpose_2 == 4,3,
                                         ifelse(df$purpose_2 == 3,4,
                                                ifelse(df$purpose_2 == 2, 5,
                                                       ifelse(df$purpose_2 == 1,6,
                                                              NA))))))


df$purpose_4r <- ifelse(df$purpose_4 == 6,1,
                        ifelse(df$purpose_4 == 5,2,
                               ifelse(df$purpose_4 == 4,3,
                                      ifelse(df$purpose_4 == 3,4,
                                             ifelse(df$purpose_4 == 2, 5,
                                                    ifelse(df$purpose_4 == 1,6,
                                                           NA))))))

df$purpose_5r <- ifelse(df$purpose_5 == 6,1,
                        ifelse(df$purpose_5 == 5,2,
                               ifelse(df$purpose_5 == 4,3,
                                      ifelse(df$purpose_5 == 3,4,
                                             ifelse(df$purpose_5 == 2, 5,
                                                    ifelse(df$purpose_5 == 1,6,
                                                           NA))))))
df$purpose_6r <- ifelse(df$purpose_6 == 6,1,
                        ifelse(df$purpose_6 == 5,2,
                               ifelse(df$purpose_6 == 4,3,
                                      ifelse(df$purpose_6 == 3,4,
                                             ifelse(df$purpose_6 == 2, 5,
                                                    ifelse(df$purpose_6 == 1,6,
                                                           NA))))))

  

df$purpose = rowMeans(df[,c("purpose_1",  "purpose_2r", "purpose_3" , "purpose_4r",
                 "purpose_5r", "purpose_6r", "purpose_7")])




#calculate intention average scores


#all intention items (1-10)

df$intentions1_7r <- ifelse(df$intentions1_7 == 7,1,
                            ifelse(df$intentions1_7 == 6,2,
                                   ifelse(df$intentions1_7 == 5,3,
                                          ifelse(df$intentions1_7 == 4,4,
                                                 ifelse(df$intentions1_7 == 3, 5,
                                                        ifelse(df$intentions1_7 == 2,6,
                                                               ifelse(df$intentions1_7 == 1,7,
                                                                      NA)))))))
df$intentions1_8r <- ifelse(df$intentions1_8 == 7,1,
                            ifelse(df$intentions1_8 == 6,2,
                                   ifelse(df$intentions1_8 == 5,3,
                                          ifelse(df$intentions1_8 == 4,4,
                                                 ifelse(df$intentions1_8 == 3, 5,
                                                        ifelse(df$intentions1_8 == 2,6,
                                                               ifelse(df$intentions1_8 == 1,7,
                                                                      NA)))))))
df$intentions1_9r <- ifelse(df$intentions1_9 == 7,1,
                            ifelse(df$intentions1_9 == 6,2,
                                   ifelse(df$intentions1_9 == 5,3,
                                          ifelse(df$intentions1_9 == 4,4,
                                                 ifelse(df$intentions1_9 == 3, 5,
                                                        ifelse(df$intentions1_9 == 2,6,
                                                               ifelse(df$intentions1_9 == 1,7,
                                                                      NA)))))))





df$intentions = rowMeans(df[,c("intentions1_1" , "intentions1_2" , "intentions1_3" , "intentions1_4" , 
                               "intentions1_5" , "intentions1_6" , "intentions1_7r" ,  "intentions1_8r" ,  
                               "intentions1_9r" , "intentions1_10")])


#intention 1, social distancing items only: 2, 4, 6, 10
df$intentions_sd = rowMeans(df[,c("intentions1_2","intentions1_4", "intentions1_6", "intentions1_10")])

#intention non sd items: 1, 3, 5, 7r, 8r, 9r
df$intentions_nsd = rowMeans(df[,c("intentions1_1","intentions1_3", "intentions1_5", "intentions1_7r", "intentions1_8r", "intentions1_9r")])

#intention hand items: 1, 7r, 8r, 9r
df$intentions_hand = rowMeans(df[,c("intentions1_1","intentions1_7r", "intentions1_8r", "intentions1_9r")])

#intention home items: 3, 5
df$intentions_home = rowMeans(df[,c("intentions1_3", "intentions1_5")])




# norms

## norms_close all (1-10)

df$norms_close1_7r <- 100-df$norms_close1_7
df$norms_close1_8r <- 100-df$norms_close1_8
df$norms_close1_9r <- 100-df$norms_close1_9

df$norms_close = rowMeans(df[,c("norms_close1_1", "norms_close1_2", "norms_close1_3", "norms_close1_4", 
"norms_close1_5", "norms_close1_6", "norms_close1_7r", "norms_close1_8r",
"norms_close1_9r", "norms_close1_10")])


# norms_close social distancing only (2 4 6 10)
df$norms_close_sd = rowMeans(df[,c("norms_close1_2", "norms_close1_4", "norms_close1_6", "norms_close1_10")])

#norms_close non sd items: 1, 3, 5, 7r, 8r, 9r
df$norms_close_nsd = rowMeans(df[,c("norms_close1_1","norms_close1_3", "norms_close1_5", "norms_close1_7r", "norms_close1_8r", "norms_close1_9r")])


#norms_close hand items: 1, 7r, 8r, 9r
df$norms_close_hand = rowMeans(df[,c("norms_close1_1","norms_close1_7r", "norms_close1_8r", "norms_close1_9r")])

#norms_close home items: 3, 5
df$norms_close_home = rowMeans(df[,c("norms_close1_3", "norms_close1_5")])




#belief
## belief_norms (1, 2, 3 (took out 4 in the purpose prereg))
df$beliefs_norms_1r <- ifelse(df$beliefs_norms_1 == 7,1,
                              ifelse(df$beliefs_norms_1 == 6,2,
                                     ifelse(df$beliefs_norms_1 == 5,3,
                                            ifelse(df$beliefs_norms_1 == 4,4,
                                                   ifelse(df$beliefs_norms_1 == 3, 5,
                                                          ifelse(df$beliefs_norms_1 == 2,6,
                                                                 ifelse(df$beliefs_norms_1 == 1,7,
                                                                        NA)))))))


df$beliefs_norms = rowMeans(df[,c("beliefs_norms_1r","beliefs_norms_2","beliefs_norms_3")])
df$beliefs_safe_self = rowMeans(df[,c("beliefs_safe_self_1","beliefs_safe_self_2", "beliefs_safe_self_3", 
                                      "beliefs_safe_self_4", "beliefs_safe_self_5")])
df$beliefs_safe_others = rowMeans(df[,c( "beliefs_safe_others_1","beliefs_safe_others_2", "beliefs_safe_others_3",
                                       "beliefs_safe_others_4", "beliefs_safe_others_5", "beliefs_safe_others_6",
                                       "beliefs_safe_others_7", "beliefs_safe_others_8")])

#clean up the subjective SES scale
df <- within(df, {
  ses_subj <- ifelse(ses_subj_1 == "On", 1,
                     ifelse(ses_subj_2 == "On", 2,
                            ifelse(ses_subj_3 == "On", 3,
                                   ifelse(ses_subj_4 == "On", 4, 
                                          ifelse(ses_subj_5 == "On", 5,
                                                 ifelse(ses_subj_6 == "On", 6, 
                                                        ifelse(ses_subj_7 == "On", 7,
                                                               ifelse(ses_subj_8 == "On", 8, 
                                                                      ifelse(ses_subj_9 == "On", 9,
                                                                             ifelse(ses_subj_10 == "On", 10, NA))))))))))
})



#subset with available data
df_raw <- df
df =subset (df,lonely_current!='NA')
df =subset (df,purpose!='NA')
df =subset (df,intentions !='NA')

df$lonely_change = df$lonely_current - df$lonely_prior
summary(df$lonely_change)

df$lonely_ave = rowMeans(df[,c("lonely_current","lonely_prior")])
summary(df$lonely_ave)


#winsorize the following variables
table(scale(df$purpose))
table(scale(df$intentions))
table(scale(df$intentions_sd))
table(scale(df$intentions_nsd))
table(scale(df$intentions_hand)) 
table(scale(df$intentions_home)) 
table(scale(df$norms_close)) 
table(scale(df$norms_close_sd)) 
table(scale(df$norms_close_home)) 
table(scale(df$beliefs_safe_self)) 
table(scale(df$beliefs_safe_others)) 
table(scale(df$lonely_change)) 
table(scale(df$house_size_curre))
table(scale(df$age))
table(scale(df$norms_close_nsd)) #no outlier 
table(scale(df$norms_close_hand )) #no outlier 
table(scale(df$beliefs_norms )) #no outlier 
table(scale(df$lonely_current)) #no outliers
table(scale(df$lonely_prior))#no outliers
table(scale(df$ses_subj))#no outliers



df=df %>%
mutate(mean = mean(purpose, na.rm = TRUE),
       sd3 = 3*sd(purpose, na.rm = TRUE),
       purpose = ifelse(purpose > mean + sd3, mean + sd3, purpose), # above --> mean - 3 * SD
       purpose = ifelse(purpose < mean - sd3, mean - sd3, purpose))%>% # below --> mean - 3 * SD

mutate(mean = mean(intentions, na.rm = TRUE),
       sd3 = 3*sd(intentions, na.rm = TRUE),
       intentions = ifelse(intentions > mean + sd3, mean + sd3, intentions), # above --> mean - 3 * SD
       intentions = ifelse(intentions < mean - sd3, mean - sd3, intentions))%>% # below --> mean - 3 * SD
  mutate(mean = mean(intentions_sd, na.rm = TRUE),
         sd3 = 3*sd(intentions_sd, na.rm = TRUE),
         intentions_sd = ifelse(intentions_sd > mean + sd3, mean + sd3, intentions_sd), # above --> mean - 3 * SD
         intentions_sd = ifelse(intentions_sd < mean - sd3, mean - sd3, intentions_sd))%>% # below --> mean - 3 * SD
  mutate(mean = mean(intentions_nsd, na.rm = TRUE),
         sd3 = 3*sd(intentions_nsd, na.rm = TRUE),
         intentions_nsd = ifelse(intentions_nsd > mean + sd3, mean + sd3, intentions_nsd), # above --> mean - 3 * SD
         intentions_nsd = ifelse(intentions_nsd < mean - sd3, mean - sd3, intentions_nsd))%>% # below --> mean - 3 * SD
  mutate(mean = mean(intentions_hand, na.rm = TRUE),
         sd3 = 3*sd(intentions_hand, na.rm = TRUE),
         intentions_hand = ifelse(intentions_hand > mean + sd3, mean + sd3, intentions_hand), # above --> mean - 3 * SD
         intentions_hand = ifelse(intentions_hand < mean - sd3, mean - sd3, intentions_hand))%>%
  mutate(mean = mean(intentions_home, na.rm = TRUE),
         sd3 = 3*sd(intentions_home, na.rm = TRUE),
         intentions_home = ifelse(intentions_home > mean + sd3, mean + sd3, intentions_home), # above --> mean - 3 * SD
         intentions_home = ifelse(intentions_home < mean - sd3, mean - sd3, intentions_home))%>%
  mutate(mean = mean(norms_close, na.rm = TRUE),
         sd3 = 3*sd(norms_close, na.rm = TRUE),
         norms_close = ifelse(norms_close > mean + sd3, mean + sd3, norms_close), # above --> mean - 3 * SD
         norms_close = ifelse(norms_close < mean - sd3, mean - sd3, norms_close))%>%
  mutate(mean = mean(norms_close_sd, na.rm = TRUE),
         sd3 = 3*sd(norms_close_sd, na.rm = TRUE),
         norms_close_sd = ifelse(norms_close_sd > mean + sd3, mean + sd3, norms_close_sd), # above --> mean - 3 * SD
         norms_close_sd = ifelse(norms_close_sd < mean - sd3, mean - sd3, norms_close_sd))%>%
  mutate(mean = mean(norms_close_home, na.rm = TRUE),
         sd3 = 3*sd(norms_close_home, na.rm = TRUE),
         norms_close_home = ifelse(norms_close_home > mean + sd3, mean + sd3, norms_close_home), # above --> mean - 3 * SD
         norms_close_home = ifelse(norms_close_home < mean - sd3, mean - sd3, norms_close_home))%>%
  mutate(mean = mean(beliefs_safe_self, na.rm = TRUE),
         sd3 = 3*sd(beliefs_safe_self, na.rm = TRUE),
         beliefs_safe_self = ifelse(beliefs_safe_self > mean + sd3, mean + sd3, beliefs_safe_self), # above --> mean - 3 * SD
         beliefs_safe_self = ifelse(beliefs_safe_self < mean - sd3, mean - sd3, beliefs_safe_self))%>%
  mutate(mean = mean(beliefs_safe_others, na.rm = TRUE),
         sd3 = 3*sd(beliefs_safe_others, na.rm = TRUE),
         beliefs_safe_others = ifelse(beliefs_safe_others > mean + sd3, mean + sd3, beliefs_safe_others), # above --> mean - 3 * SD
         beliefs_safe_others = ifelse(beliefs_safe_others < mean - sd3, mean - sd3, beliefs_safe_others))%>%
  mutate(mean = mean(lonely_change, na.rm = TRUE),
         sd3 = 3*sd(lonely_change, na.rm = TRUE),
         lonely_change = ifelse(lonely_change > mean + sd3, mean + sd3, lonely_change), # above --> mean - 3 * SD
         lonely_change = ifelse(lonely_change < mean - sd3, mean - sd3, lonely_change))%>%
  mutate(mean = mean(house_size_curre, na.rm = TRUE),
         sd3 = 3*sd(house_size_curre, na.rm = TRUE),
         house_size_curre = ifelse(house_size_curre > mean + sd3, mean + sd3, house_size_curre), # above --> mean - 3 * SD
         house_size_curre = ifelse(house_size_curre < mean - sd3, mean - sd3, house_size_curre))%>%
  mutate(mean = mean(age, na.rm = TRUE),
         sd3 = 3*sd(age, na.rm = TRUE),
         age = ifelse(age > mean + sd3, mean + sd3, age), # above --> mean - 3 * SD
         age = ifelse(age < mean - sd3, mean - sd3, age))
```

# demographics
```{r}
summary(df$age)
sd(df$age)
table (df$gender)
table (df$race)
```

```{r}
#The current and pre-pandemic levels of loneliness were highly correlated
cor.test(df$lonely_current, df$lonely_prior)

# crombach's alpha
df_purpose <- df_raw[ , c("purpose_1", "purpose_2r", "purpose_3", "purpose_4r", "purpose_5r", "purpose_6r", "purpose_7")]    
alpha(df_purpose)

df_intention <- df_raw[ , c("intentions1_1" , "intentions1_2" , "intentions1_3" , "intentions1_4" , 
                               "intentions1_5" , "intentions1_6" , "intentions1_7r" ,  "intentions1_8r" ,  
                               "intentions1_9r" , "intentions1_10")]    
alpha(df_intention)

```

# define function to make results table
```{r}
make_table = function(model) {
  require(broom)
  require(knitr)
  
  print(data.frame(R2 = summary(model)$r.squared,
             adjusted_R2 = summary(model)$adj.r.squared,
             df = summary(model)$df[2]) %>%
    knitr::kable(format = "pandoc", digits = 2))
    
  print(model %>%
    broom::tidy(conf.int = TRUE) %>%
    mutate(p.value = ifelse(p.value < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p.value))),
           `95% CI` = sprintf("%.2f, %.2f", conf.low, conf.high),
           term = gsub("as.factor", "", term)) %>%
    select(-contains("conf")) %>%
    rename("b" = estimate,
           "SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(term, b, `95% CI`, everything()) %>%
    knitr::kable(format = "pandoc", digits = 2))
}
```

# Purpose in life Predicting Loneliness and COVID-Preventive Intentions {.tabset}
## H1a
Higher self-reported purpose in life will be associated with less perceived loneliness.

As preregistered, across participants, higher self-reported purpose in life was associated with lower loneliness, for both the current

```{r}
test <- lm(lonely_current ~ purpose+as.factor(condition), data=df)#in the main text

lm.beta(test)
summary(test)
make_table(test)

test <- lm(lonely_prior ~ purpose+as.factor(condition), data=df)#in the main text

lm.beta(test)
summary(test)
make_table(test)
```


## H2.

Higher self-reported purpose in life will be associated with more positive responses to COVID-19 related measures, including intentions, norms, and beliefs.

```{r}
test <- lm(intentions~purpose+as.factor(condition), df) #in the main text

lm.beta(test)
summary(test)
make_table(test)

```

# Loneliness Predicting COVID Preventive Intentions

Higher levels of loneliness was associated with lower COVID preventive intentions, for both the current 

```{r}
test <- lm(intentions~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(intentions~lonely_prior+as.factor(condition), df)

summary(test)
make_table(test)
```

# Purpose in Life Moderating the Relationship Between Age and Lonelines {.tabset}

## H1b.

Age will be tested as a potential moderator for H1a, such that higher purpose is more strongly associated with less loneliness for older adults compared to younger adults


First, we found that age was negatively associated with loneliness, such that older compared to younger individuals reported feeling less lonely at present 

```{r}
test <- lm(lonely_current ~ age+as.factor(condition), df)#in the main text

summary(test)
make_table(test)

test <- lm(lonely_prior ~ age+as.factor(condition), df)#in the main text

summary(test)
make_table(test)
```

Contrary to our preregistered prediction, we did not detect a significant interaction between purpose in life and age in predicting current levels of loneliness 

```{r}
test <- lm(lonely_current~ age*purpose+as.factor(condition), df)

summary(test)
make_table(test)

#simple slopes analysis
print(purpose_low<- round((mean(df$purpose) - sd(df$purpose)),1))
print(purpose_mid<- round((mean(df$purpose)),1))
print(purpose_high <- round((mean(df$purpose) + sd(df$purpose)),1))


df$lonely_cen = df$lonely_current - mean(df$lonely_current,na.rm=T)
df$age_cen = df$age - mean(df$age,na.rm=T)
df$purpose_cen = df$purpose - mean(df$purpose,na.rm=T)
df$intentions_cen = df$intentions - mean(df$intentions,na.rm=T)
#df$lonely_prior_cen = df$lonely_prior - mean(df$lonely_prior,na.rm=T)

df$purpose_low <- df$purpose_cen + sd(df$purpose_cen, na.rm=T)
df$purpose_high <- df$purpose_cen - sd(df$purpose_cen, na.rm=T)
```

At higher and mean levels of purpose in life, older age predict less loneliness, at one standard deviation above the mean

```{r}
test <-lm(lonely_cen~ purpose_high *age_cen+ as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(lonely_cen~ purpose_cen *age_cen+ as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(lonely_cen~ purpose_low *age_cen+ as.factor(condition), df)

summary(test)
make_table(test)

#We also conducted a robustness check by dividing the sample at the median purpose score 
purpose_high <- subset(df, purpose >= median(df$purpose))
purpose_low <- subset(df, purpose < median(df$purpose))

test <-lm(lonely_cen~ age_cen+ as.factor(condition), purpose_high)

summary(test)
make_table(test)

test <-lm(lonely_cen~ age_cen+ as.factor(condition), purpose_low)

summary(test)
make_table(test)
```

# Exploratory Analyses: The Relationship between Loneliness and COVID Preventive Intentions at Different Levels of Purpose in Life 
```{r}
test <-lm(intentions_cen~ purpose_low *lonely_cen+ as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(intentions_cen~ purpose_cen *lonely_cen+ as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(intentions_cen~ purpose_high *lonely_cen+ as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(intentions ~ lonely_cen+ as.factor(condition), purpose_low)

summary(test)
make_table(test)

test <-lm(intentions ~ lonely_cen+ as.factor(condition), purpose_high)

summary(test)
make_table(test)
```

# TABLE & FIGURE {.tabset}
## Figure 1. 
```{r}
# A.Simple slopes analysis showing the relationship between age and current loneliness at high (one standard deviation above the mean), mean, and low ( one standard deviation below the mean) levels of purpose in life. 
test <- lm(lonely_current ~ age*purpose +as.factor(condition) , df)
interact_plot(test, pred = age, modx = purpose, interval = TRUE, 
              int.type = "confidence", int.width = 0.95) 

#B. Simple slopes analysis showing the relationship between purpose in life and current loneliness across age, at one standard deviation below the mean (26.4 years), mean (37.7 years), one standard deviation above the mean (49 years), and two standard deviations above the mean (60.3 years) ages.
interact_plot(test, pred = purpose, modx = age, interval = TRUE, 
              int.type = "confidence", int.width = 0.95, modx.values = c(26.4, 37.7, 49, 60.3)) 
```

## Table 1
```{r}
h3=df %>%
  dplyr::select("purpose","lonely_current","lonely_prior","intentions", "age", "gender", "ses_subj", "house_size_curre")
M <- Hmisc::rcorr(as.matrix(h3))
corrplot(M$r, p.mat = M$P, insig = "label_sig",
         sig.level = c(.001, .05), pch.cex=0.9, pch.col = "white",
         method="color", type="lower")

#table 1. correlation matrix
cor.test(df$purpose, df$lonely_current)
cor.test(df$purpose, df$lonely_prior)
cor.test(df$purpose, df$intentions)
cor.test(df$purpose, df$age)
cor.test(df$purpose, df$gender)
cor.test(df$purpose, df$ses_subj)
cor.test(df$purpose, df$house_size_curre)

cor.test(df$lonely_current, df$lonely_prior)
cor.test(df$lonely_current, df$intentions)
cor.test(df$lonely_current, df$age)
cor.test(df$lonely_current, df$gender)
cor.test(df$lonely_current, df$ses_subj)
cor.test(df$lonely_current, df$house_size_curre)

cor.test(df$lonely_prior, df$intentions)
cor.test(df$lonely_prior, df$age)
cor.test(df$lonely_prior, df$gender)
cor.test(df$lonely_prior, df$ses_subj)
cor.test(df$lonely_prior, df$house_size_curre)

cor.test(df$intentions, df$age)
cor.test(df$intentions, df$gender)
cor.test(df$intentions, df$ses_subj)
cor.test(df$intentions, df$house_size_curre)

cor.test(df$age, df$gender)
cor.test(df$age, df$ses_subj)
cor.test(df$age, df$house_size_curre)

cor.test(df$gender, df$ses_subj)
cor.test(df$gender, df$house_size_curre)

cor.test(df$ses_subj, df$house_size_curre)
```

## Table 2 {.tabset}
### M1: Purpose in life → Loneliness (current)
```{r}
test <- lm(lonely_current ~ purpose+as.factor(condition), data=df)#in the main text

lm.beta(test)
summary(test)
make_table(test)
```

### M2: Purpose in life  → Loneliness (pre-pandemic)
```{r}
test <- lm(lonely_prior ~ purpose+as.factor(condition), data=df)#in the main text

lm.beta(test)
summary(test)
make_table(test)
```

### M3: Purpose in life → COVID preventive intentions
```{r}
test <- lm(intentions~purpose+as.factor(condition), df) #in the main text

lm.beta(test)
summary(test)
make_table(test)
```

### M4: Loneliness (current) → COVID preventive intentions
```{r}
test <- lm(intentions~lonely_current+as.factor(condition), df)

lm.beta(test)
summary(test)
make_table(test)
```

### M5: Loneliness (pre-pandemic) → COVID preventive intentions
```{r}
test <- lm(intentions~lonely_prior+as.factor(condition), df)

lm.beta(test)
summary(test)
make_table(test)
```

### M6: Age → Loneliness (current)
```{r}
test <- lm(lonely_current ~ age+as.factor(condition), df)#in the main text

lm.beta(test)
summary(test)
make_table(test)
```

### M7: Age → Loneliness (pre-pandemic)
```{r}
test <- lm(lonely_prior ~ age+as.factor(condition), df)#in the main text

lm.beta(test)
summary(test)
make_table(test)
```

### M8: Purpose in life * Age → Loneliness
```{r}
test <- lm(lonely_current~ purpose*age+as.factor(condition), df)

lm.beta(test)
summary(test)
make_table(test)
```

### M9: Purpose in life * Loneliness → COVID preventive intentions
```{r}
test <- lm(intentions~ purpose*lonely_current+as.factor(condition), df)

lm.beta(test)
summary(test)
make_table(test)
```

# SUPPLEMENTALS {.tabset}
## SI2

Associations between self-reported purpose in life and responses to COVID-19 related measures, including norms and beliefs. 

Across participants, higher self-reported purpose in life was associated with higher perceived norms about COVID-19 preventative behaviors among social ties

```{r}
test <-lm(norms_close~purpose+as.factor(condition), df)

summary(test)
make_table(test)
```


Further, higher purpose in life was associated with greater beliefs that taking COVID preventative measures will be approved by their social ties 

```{r}
test <-lm(beliefs_norms~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(beliefs_safe_others~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <-lm(beliefs_safe_self~purpose+as.factor(condition), df)

summary(test)
make_table(test)

```

## SI3
COVID-related outcomes specifically related to social distancing.

First, higher purpose in life was associated with each of our measured prevention behaviors, including: greater intentions to maintain social distance 

```{r}
test <- lm(intentions_sd~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(intentions_hand~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(intentions_home~purpose+as.factor(condition), df)

summary(test)
make_table(test)
```


Higher purpose also predicted higher perceptions about the normative approval of protective health behaviors including social distancing 

```{r}
test <- lm(norms_close_sd~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(norms_close_hand~purpose+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(norms_close_home~purpose+as.factor(condition), df)

summary(test)
make_table(test)
```

Next, we tested whether the association between loneliness and COVID preventive intentions was driven by specific types of protective behavior.  

Higher loneliness predicted worse outcomes for each of the COVID-19 related subcategory behavior: higher loneliness was associated with

```{r}
test <- lm(intentions_sd~ lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(intentions_hand~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(intentions_home~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)
```


Higher loneliness also predicted lower perceptions about the normative approval of protective health behaviors including social distancing 
```{r}
test <- lm(norms_close_sd~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(norms_close_hand~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(norms_close_home~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

```

## SI4
Potential covariates for analysis including loneliness.

```{r}
summary(lm(lonely_current ~ purpose+as.factor(condition)+house_size_curre+as.factor(gender)+ses_subj, data=df))#continued to be sig
summary(lm(intentions~lonely_current+as.factor(condition)+house_size_curre+as.factor(gender)+ses_subj, df))#continued to be ns
summary(lm(lonely_current~age+as.factor(condition)+house_size_curre+as.factor(gender)+ses_subj, df))#continued to be ns
```

## SI5
Associations between perceived loneliness and responses to COVID-19 related measures.

```{r}
test <- lm(norms_close~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(beliefs_norms~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(beliefs_safe_others~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

test <- lm(beliefs_safe_self~lonely_current+as.factor(condition), df)

summary(test)
make_table(test)

```

## SI6
Subsetting the sample to run analyses for the group that were not exposed to messages

In this subsample, higher purpose was associated with lower current levels of loneliness as in the main analysis

```{r}
df2 =subset (df,condition=='no message control')

test <-lm(lonely_current ~ purpose, df2)

summary(test)
make_table(test)
```

Higher purpose was also associated with higher COVID preventive intentions in this subsample

```{r}
test <-lm(intentions~purpose, df2)

summary(test)
make_table(test)

test <-lm(intentions_sd~purpose, df2)

summary(test)
make_table(test)

test <-lm(norms_close~purpose, df2)

summary(test)
make_table(test)

test <-lm(norms_close_sd~purpose, df2)

summary(test)
make_table(test)

test <-lm(beliefs_norms~purpose, df2)

summary(test)
make_table(test)

test <-lm(beliefs_safe_others~purpose, df2)

summary(test)
make_table(test)

test <-lm(beliefs_safe_self~purpose, df2)

summary(test)
make_table(test)
```

Consistent with main results, higher loneliness was associated with lower COVID preventive intentions 

```{r}
test <-lm(intentions ~ lonely_current, df2)

summary(test)
make_table(test)

test <-lm(intentions_sd ~ lonely_current, df2)

summary(test)
make_table(test)
```

## Figure SI

Exploratory simple slopes at four levels of age across three levels of purpose in life.

```{r}
test <- lm(intentions ~ lonely_current*age*purpose +as.factor(condition) , df)
interact_plot(test, pred = lonely_current, modx = age, mod2=purpose, interval = TRUE, 
              int.type = "confidence", int.width = 0.95, modx.values = c(26.4, 37.7, 49, 60.3)) 




summary(lm(intentions_home ~ lonely_current +as.factor(condition) , df))
```

